A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-15 survey.tex
Quick fixes on the bot descriptions to reflect the figure changes

\begin{itemize}
\item
  BroodwarBotQ\footnote{\url{http://github.com/SnippyHolloW/BroodwarBotQ}}:
  uses  abstraction for  {\em combat}, and  divide-and-conquer for
  {\em economy}  and  {\em intelligence  gathering}. To  avoid  conflicts
  between modules (since  the individual tasks of each  of the modules
  are not completely independent), BBQ uses an arbitrator.
\item  Nova\footnote{\url{http://nova.wolfwork.com/}}:  is similar  in
  design as  BroodwarBotQ, and uses  abstraction for {\em combat},
  and  divide-and-conquer for  {\em economy}.  The differences  are
  that Nova does not have  an arbitrator to resolve conflicts, but has
  a  higher-level   module  ({\em  strategy   manager}),  which  posts
  information to the blackboard that the rest of modules follow (thus,
  making use of abstraction).
\item
  UAlbertaBot\footnote{\url{http://code.google.com/p/ualbertabot/}}:
  also  uses abstraction  in  {\em combat} like  the previous  two
  bots. But it  also uses it in {|em economy}: as  can be seen, the
  production manager sends commands to the building manager, who is in
  charge   of   producing   the   buildings.  This   bot   also   uses
  divide-and-conquer, and  tasks like scouting  and resource gathering
  are managed by separate, independent modules.
\item       Skynet\footnote{\url{http://code.google.com/p/skynetbot/}}:
  makes     extensive     use      of     both     abstraction     and
  divide-and-conquer.  We  can see a  high level module  that issues commands  to a
  series of  tactics modules. The  collection of tactic  modules queue
  {\em  tasks} (that  are analogous  to the  abstract actions  used in
  SPAR).  Each different  task has  a specific  low level  module that
  knows how to  execute it. Thus, Skynet uses  a 3 layered abstraction
  hierarchy,  and uses  divide-and-conquer  in all  levels except  the
  highest.
\item
  SPAR\footnote{\url{http://www.planiart.usherbrooke.ca/projects/spar/}}:
  only uses abstraction. Its high-level module determines the strategy
  to  use,  and  the  tactical  decision  module  divides  it  into  a
  collection  of {\em  abstract  actions}, that  are  executed by  the
  lower-level modules.
\item  AIUR\footnote{\url{http://code.google.com/p/aiurproject/}}:  is
  mainly divide-and-conquer oriented, for {\em economy} as well as for {\em combat},
  with a  slight abstraction on  macro due to a  SpendManager deciding
  how  to  spend  and  share  resources  among  Base,  Production  and
  Construction Managers.  At the beginning of a  game, the MoodManager
  initializes  a  ``mood''  which  will  influence  both  tactics  and
  strategy. {\em Combat} is divided into three  independent managers: the
  {\em  Defense Manager},  controlling  military units  when there  is
  nothing special, the {\em  Under Attack Manager}, activated when the
  opponent is attacking our bases,  and the {\em Army Manager}, taking
  control of units when it is time to attack, following a timing given
  by the  current mood. This bot  does not manage however  any kind of
  reactive controls so far.
\item  BTHAI\footnote{\url{http://code.google.com/p/bthai/}}:  uses  a
  two-tier  abstraction hierarchy,  where a  collection  of high-level
  modules command a collection of lower-level agents in charge of each
  of  the units.  At  the high-level,  BTHAI uses  divide-and-conquer,
  having   multiple  high-level  modules   issuing  commands   to  the
  lower-level units.
\end{itemize}

>>>>

\begin{itemize}
\item
  BroodwarBotQ\footnote{\url{http://github.com/SnippyHolloW/BroodwarBotQ}}:
  uses  abstraction for  {\em combat}, and  divide-and-conquer for
  {\em economy}  and  {\em intelligence  gathering}. To  avoid  conflicts
  between modules (since  the individual tasks of each  of the modules
  are not completely independent), BBQ uses an arbitrator.
\item  Nova\footnote{\url{http://nova.wolfwork.com/}}:  is similar  in
  design as  BroodwarBotQ, and uses  abstraction for {\em combat},
  and  divide-and-conquer for  {\em economy}.  The differences  are
  that Nova does not have  an arbitrator to resolve conflicts, but has
  a  higher-level   module  ({\em  strategy   manager}),  which  posts
  information to the blackboard that the rest of modules follow (thus,
  making use of abstraction).
\item
  UAlbertaBot\footnote{\url{http://code.google.com/p/ualbertabot/}}:
  also  uses abstraction  in  {\em combat} like  the previous  two
  bots. But it  also uses it in {|em economy}: as  can be seen, the
  production manager sends commands to the building manager, who is in
  charge   of   producing   the   buildings.  This   bot   also   uses
  divide-and-conquer, and  tasks like scouting  and resource gathering
  are managed by separate, independent modules.
\item       Skynet\footnote{\url{http://code.google.com/p/skynetbot/}}:
  makes     extensive     use      of     both     abstraction     and
  divide-and-conquer.  We  can see a  high level module  that issues commands  to a
  series of  tactics modules. The  collection of tactic  modules queue
  {\em  tasks} (that  are analogous  to the  abstract actions  used in
  SPAR).  Each different  task has  a specific  low level  module that
  knows how to  execute it. Thus, Skynet uses  a 3 layered abstraction
  hierarchy,  and uses  divide-and-conquer  in all  levels except  the
  highest.
\item
  SPAR\footnote{\url{http://www.planiart.usherbrooke.ca/projects/spar/}}:
  only uses abstraction. Its high-level module determines the strategy
  to  use,  and  the  tactical  decision  module  divides  it  into  a
  collection  of {\em  abstract  actions}, that  are  executed by  the
  lower-level modules.
\item  AIUR\footnote{\url{http://code.google.com/p/aiurproject/}}:  is
  mainly divide-and-conquer oriented,
  with a  slight abstraction on  {\em economy} due to a  SpendManager deciding
  how  to  spend  and  share  resources  among  Base,  Production  and
  Construction Managers.  At the beginning of a  game, the MoodManager
  initializes  a  ``mood''  which  will  influence  both  tactics  and
  strategy. {\em Combat} is divided into three  independent managers: the
  {\em  Defense Manager},  controlling  military units  when there  is
  nothing special, the {\em  Under Attack Manager}, activated when the
  opponent is attacking our bases,  and the {\em Army Manager}, taking
  control of units when it is time to attack, following a timing given
  by the  current mood. This bot  does not manage however  any kind of
  reactive controls so far.
\item  BTHAI\footnote{\url{http://code.google.com/p/bthai/}}:  uses  a
  two-tier  abstraction hierarchy,  where a  collection  of high-level
  modules command a collection of lower-level agents in charge of each
  of  the units.  At  the high-level,  BTHAI uses  divide-and-conquer,
  having   multiple  high-level  modules   issuing  commands   to  the
  lower-level units.
\end{itemize}
